I can see clearly now: reinterpreting statistical significance

### 2018-08-03 doc.tex
Update doc.tex

>>>>

\mk{Not exactly what we are talking about here, but there are a few good ideas/quotes in this blog post: https://rapidecology.com/2018/05/02/abandon-anova-type-experiments/}

`` I’d like to propose that simple “comparison of means” experiments (those analyzed with a t-test or ANOVA) train our brains to think that this is the goal of science – to discover if an effect exists. --- But the goal of our science should be mechanistic and predictive models that make quantitative predictions that might be tested with experiments.''

``The absurdity of the t-test or  ANOVA way of doing science is apparent if something like temperature and CO2 are the experimental factors – for example in the many global climate change studies. What in ecology or physiology or cell biology is not related to temperature and CO2?''
